Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
social p

<!-- social scale -->
Social scale is essential consideration for social network analysis
[@Castles_2014; @Carter_2015; @Farine_2015a]. For example, networks can be
constructed based on fine-scale social interactions (e.g. grooming or
aggression), social associations (e.g. group membership or proximity), or
spatial or home range overlap. Here, we define social associations in a series
of proximity-based social networks based on a series of social distance
thresholds. <!-- up to here-->Increasing the social distance threshold resulted in an
increase in graph strength across all three habitat layers  (Figure
\@ref(fig:socres)). <!-- This means blah blah for different types of
interactions.--> However, habitat layers differed in their response to
increasing social distance threshold, with open and foraging with a larger
increase in graph strength and greater variation across individuals. <!-- What
could this mean biologically? --> These results emphasize that multilayer
network metrics are directly influenced by social scale. In extension, caribou
relocations could be classified into behavioural states using hidden Markov
models to explore the influence of behavioural states on social scale in a
multilayer network [see @Jones_2020].
<!-- social scale -->

<!-- habitat+social -->
Social structure and habitat selection are intimately related: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Johnson (1980) identified four
orders of habitat selection: (1) the geographical range of a species, (2) the
home range of an individual, the (3) habitat patches within the home range and
(4) specific resources within a habitat patch. Kie et al. [-@Kie_2002] found
that, independently, third order of selection was insufficient for capturing
landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a
scale larger than their home range size. Moving past this hierarchical
perspective, Mayor (2007) emphasized the importance of considering a broad
continuum of scales to reveal scale-dependent selection and avoid the bias of
predefined scales assumed to be associated with certain behaviours.

>>>>

<!-- social scale -->
Social scale is an essential consideration for social network analysis
[@Castles_2014; @Carter_2015; @Farine_2015a]. For example, networks can be
constructed based on fine-scale social interactions (e.g. grooming or
aggression), social associations (e.g. group membership or proximity), or
spatial or home range overlap. Here, we define social associations using a series
of social distance thresholds to generate proximity-based social networks. 
Across network layers, increasing the social distance threshold resulted in
an increase in graph strength (Figure
\@ref(fig:socres)). Specifically, the strength of social associations across 
habitat layers, with open and foraging habitats demonstrating a more pronounced
increase in graph strength as well as greater variation across individuals. 
These results emphasize that multilayer network metrics are directly influenced
by social scale. An extension of this analysis could be to incorporate 
behavioural states to explore the influence of social scale on patterns of 
association or interaction across habitat and behavioural layers [e.g. 
using focal observations or hidden Markov Models see @Muller_2018; @Jones_2020].
<!-- social scale -->

<!-- spatial -->
Habitat selection, the use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009].

Social structure and habitat selection are intimately related: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007].  Johnson (1980) identified four
orders of habitat selection: (1) the geographical range of a species, (2) the
home range of an individual, the (3) habitat patches within the home range and
(4) specific resources within a habitat patch. Kie et al. [-@Kie_2002] found
that, independently, third order of selection was insufficient for capturing
landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a
scale larger than their home range size. Moving past this hierarchical
perspective, Mayor (2007) emphasized the importance of considering a broad
continuum of scales to reveal scale-dependent selection and avoid the bias of
predefined scales assumed to be associated with certain behaviours.
